### 2018-11-10 VV556/HW7/submission.tex
add ex2

		\item

		\item

\section{Exercise7.2}
	\begin{enumerate}
		\item

		\item

		\item

		\item

		\item

>>>>

		\item 
			Not figured out...
		\item
			\begin{equation}
				Ru = \lambda u
			\end{equation} 
			Denote $u = (a_0, a_1, ..., a_n, ...)$, then
			\begin{equation}
				\begin{aligned}
					0 &= \lambda a_0\\
					a_0 &= \lambda a_1\\
					...\\
				\end{aligned}
			\end{equation}
	\end{enumerate}

\section{Exercise7.2}
	\begin{enumerate}
		\item 
			\begin{proof}
				Take a subset of the domain of $L^{-1}$, which is denoted as $M$ and is defined as
				\begin{equation}
					M = \Big\{u \in L^2\big([0, 1]\big) \Big| \exists \xi >0 \  \forall x \in [0, \xi] \ u(x) = 0\Big\}
				\end{equation}
				Given any $u(x) \in L^2$, then
				\begin{equation}
					\int_{0}^{1} u^2(x) dx < \infty
				\end{equation}
				Hence $u(x)$ is bounded over $[0, 1]$. \\
				Let 
				\begin{equation}
					T \triangleq \sup \limits_{x\in [0, 1]} |u(x)|
				\end{equation}
				then, $\forall \epsilon > 0$, $\exists v \in M $ s.t.
				\begin{equation}
					v(x) = \Bigg\{\begin{aligned}
					0, &\quad x \in [0, \delta]\\
					u(x), &\quad x \in (\delta, 1]
					\end{aligned}
				\end{equation}
				where $\delta = \frac{\epsilon}{T^2}$. Therefore
				\begin{equation}
					d(u, v) \triangleq ||u-v||_2 = \int_{0}^{1} [u(x) - v(x)]^2 dx = \int_{0}^{\delta} u^2(x) dx \leq T^2 \delta = \epsilon
				\end{equation}
				which indicates that $M$ is dense in $L^2$, so do the domain of $L^{-1}$.
			\end{proof}
		\item 
			\begin{proof}
				\begin{equation}
					||L|| = \sup_{u\in L^2}\frac{||Lu||_2}{||u||_2} = \sup_{u\in L^2}\frac{||xu(x)||_2}{||u(x)||_2} = \sup_{u\in L^2}\frac{|x| ||u||_2}{||u||_2} = \sup_{x\in [0, 1]} |x| = 1
				\end{equation}
				and
				\begin{equation}
					||L^{-1}|| = \sup_{u\in L^2}\frac{||L^{-1}u||_2}{||u||_2} = \sup_{x\in [0, 1]} \frac{1}{|x|} = \infty
				\end{equation}
				hence $L^{-1}$ is unbounded.
			\end{proof}
		\item 
			The state of $L$ is $(I, 1_n)$.\\
			The state of $L^{-1}$ is $(I, 2_c)$.
		\item 
			Yes
		\item 
			Since
			\begin{equation}
				[(L - \lambda I)u] (x) = (Lu)(x) - \lambda u(x) = (x-\lambda) u(x)
			\end{equation}
			The inverse of $(L - \lambda I)$ always exists, therefore $\sigma(L) = \emptyset$.
	\end{enumerate}
